---
title: "Quiz1"
author: "Aasish Agarwal"
date: "Monday, December 22, 2014"
output: html_document
runtime: shiny
---

# Week 1 Quiz Help

* Warning: The hard deadline has passed. You can attempt it, but you will not get credit for it. You are welcome to try it as a learning exercise.

In accordance with the Coursera Honor Code, I (Aasish Agarwal) certify that the answers here are my own work.

## Question 1
Which of the following is a principle of analytic graphics?

#) Show comparisons
#) Only do what your tools allow you to do
#) Show box plots (univariate summaries)
#) Make judicious use of color in your scatterplots
#) Don't plot more than two variables at at time

```{r, echo=FALSE}
cat("Show comparisons")
```

## Question 2
What is the role of exploratory graphs in data analysis?

#) Axes, legends, and other details are clean and exactly detailed.
#) The goal is for personal understanding.
#) They are used in place of formal modeling.
#) They are made for formal presentations.

```{r, echo=FALSE}
cat("The goal is for personal understanding")
```


## Question 3
Which of the following is true about the base plotting system?

#) The system is most useful for conditioning plots.
#) Plots are created and annotated with separate functions
#) Plots are typically created with a single function call
#) Margins and spacings are adjusted automatically depending on the type of plot and the data

```{r, echo=FALSE}
cat("Plots are created and annotated with separate function")
```


## Question 4
Which of the following is an example of a valid graphics device in R?

#) A Microsoft Word document
#) A socket connection
#) The keyboard
#) A PNG file

```{r, echo=FALSE}
cat("A PNG file")
```

## Question 5
Which of the following is an example of a vector graphics device in R?

#) JPEG
#) GIF
#) Postscript
#) PNG

```{r, echo=FALSE}
cat("Postscript")
```

## Question 6
Bitmapped file formats can be most useful for

#) Plots that are not scaled to a specific resolution
#) Plots that require animation or interactivity
#) Scatterplots with many many points
#) Plots that may need to be resized

```{r, echo=FALSE}
cat("Scatterplots with many many points")
```


## Question 7
Which of the following functions is typically used to add elements to a plot in the base graphics system?

#) plot()
#) boxplot()
#) hist()
#) text()

```{r, echo=FALSE}
cat("text()")
```

## Question 8
Which function opens the screen graphics device for the Mac?

#) png()
#) bitmap()
#) quartz()
#) pdf()

```{r, echo=FALSE}
cat("quartz()")
```

## Question 9
What does the 'pch' option to par() control?

#) the orientation of the axis labels on the plot
#) the plotting symbol/character in the base graphics system
#) the line width in the base graphics system
#) the size of the plotting symbol in a scatterplot

```{r, echo=FALSE}
cat("the plotting symbol/character in the base graphics system")
```

## Question 10
If I want to save a plot to a PDF file, which of the following is a correct way of doing that?

#) Open the screen device with quartz(), construct the plot, and then close the device with dev.off().
#) Open the PostScript device with postscript(), construct the plot, then close the device with dev.off().
#) Construct the plot on the PNG device with png(), then copy it to a PDF with dev.copy2pdf().
#) Construct the plot on the screen device and then copy it to a PDF file with dev.copy2pdf()

```{r, echo=FALSE}
cat("Construct the plot on the screen device and then copy it to a PDF file with dev.copy2pdf()")
```
