---
title: "Quiz1"
author: "Aasish Agarwal"
date: "Monday, December 22, 2014"
output: html_document
runtime: shiny
---
# Week 1 Quiz Help

* Warning: The hard deadline has passed. You can attempt it, but you will not get credit for it. You are welcome to try it as a learning exercise.

In accordance with the Coursera Honor Code, I (Aasish Agarwal) certify that the answers here are my own work.

## Question 1
Which of the following is a principle of analytic graphics?

1. Show comparisons
1. Only do what your tools allow you to do
1. Show box plots (univariate summaries)
1. Make judicious use of color in your scatterplots
1. Don't plot more than two variables at at time

```{r, echo=FALSE}
cat("Show comparisons")
```

## Question 2
What is the role of exploratory graphs in data analysis?

1) Axes, legends, and other details are clean and exactly detailed.
1) The goal is for personal understanding.
1) They are used in place of formal modeling.
1) They are made for formal presentations.

```{r, echo=FALSE}
cat("The goal is for personal understanding")
```


## Question 3
Which of the following is true about the base plotting system?

1) The system is most useful for conditioning plots.
1) Plots are created and annotated with separate functions
1) Plots are typically created with a single function call
1) Margins and spacings are adjusted automatically depending on the type of plot and the data

```{r, echo=FALSE}
cat("Plots are created and annotated with separate function")
```


## Question 4
Which of the following is an example of a valid graphics device in R?

1) A Microsoft Word document
1) A socket connection
1) The keyboard
1) A PNG file

```{r, echo=FALSE}
cat("A PNG file")
```

## Question 5
Which of the following is an example of a vector graphics device in R?

1) JPEG
1) GIF
1) Postscript
1) PNG

```{r, echo=FALSE}
cat("Postscript")
```

## Question 6
Bitmapped file formats can be most useful for

1) Plots that are not scaled to a specific resolution
1) Plots that require animation or interactivity
1) Scatterplots with many many points
1) Plots that may need to be resized

```{r, echo=FALSE}
cat("Scatterplots with many many points")
```


## Question 7
Which of the following functions is typically used to add elements to a plot in the base graphics system?

1) plot()
1) boxplot()
1) hist()
1) text()

```{r, echo=FALSE}
cat("text()")
```

## Question 8
Which function opens the screen graphics device for the Mac?

1) png()
1) bitmap()
1) quartz()
1) pdf()

```{r, echo=FALSE}
cat("quartz()")
```

## Question 9
What does the 'pch' option to par() control?

1) the orientation of the axis labels on the plot
1) the plotting symbol/character in the base graphics system
1) the line width in the base graphics system
1) the size of the plotting symbol in a scatterplot

```{r, echo=FALSE}
cat("the plotting symbol/character in the base graphics system")
```

## Question 10
If I want to save a plot to a PDF file, which of the following is a correct way of doing that?

1) Open the screen device with quartz(), construct the plot, and then close the device with dev.off().
1) Open the PostScript device with postscript(), construct the plot, then close the device with dev.off().
1) Construct the plot on the PNG device with png(), then copy it to a PDF with dev.copy2pdf().
1) Construct the plot on the screen device and then copy it to a PDF file with dev.copy2pdf()

```{r, echo=FALSE}
cat("Construct the plot on the screen device and then copy it to a PDF file with dev.copy2pdf()")
```
